Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Updated experiments table data.

\begin{figure}[H]
\centering
\begin{tabular}{l | r l r l}
Benchmark              & Base     &         & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    &         & 46\,s   & \\
SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
SpringMassDamper       &          &         &         & 
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end}
\vspace{0.5em}

>>>>

\begin{figure}[H]
\centering
\begin{tabular}{l | r r l}
Benchmark              & Base     & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    & 46\,s   & \\
SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
SpringMassDamper       & 28\,s    & \xmark  &
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
\vspace{0.5em}
